### 2024-11-11 conteudo/preliminar/results.tex
Add tool in cronogram
add commentary about tool improv

\input{conteudo/preliminar/cronograma}
\todo[inline]{Atualizar o cronograma, alocando tempo para evolucao da ferramenta}

@@

\todo[inline]{colocar aqui também algo da evolucao da ferramenta que sera feito até o final do mestrado}

>>>>

\input{conteudo/preliminar/cronograma}
\todo[inline]{Atualizar o cronograma, alocando tempo para evolucao da ferramenta (DONE?) }

@@

Our upcoming tasks also include implementing improvements to our proposed tool. 
While the tool’s current state allowed us to conduct the experiments described in 
Chapter \ref{cha:method},
it is not yet adequately user-friendly or manageable for external users. 
To achieve our complementary goal of providing a solution for code duplication 
in the kernel, we plan to improve the documentation, refine the code structure, 
and address any issues we encounter along the way, providing the Linux community 
with a way to tackle the issue.

\todo[inline]{colocar aqui também algo da evolucao da ferramenta que sera feito até o final do mestrado (DONE?) }
